Covariate analysis of UFL-Mayo-ISB RNASeq reprocessed counts (both cerebellum and temporal cortex) with SVA adjustments

### 2016-05-29 code/Rmd/Mayo_RNASeq_SVA_Reprocessed.Rmd
Minor bug fix

num.sv2 = num.sv(EXPR$filteredExprMatrix$COUNT, MODEL1, method = 'be', seed = 123456)
NUM.SV = min(num.sv1, num.sv2)

SURR.VAR = svaseq(EXPR$filteredExprMatrix$counts, MODEL1, MODEL0, n.sv = NUM.SV, method = "two-step", B = 30)$sv
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])

>>>>

num.sv2 = num.sv(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, method = 'be', seed = 123456)
NUM.SV = min(num.sv1, num.sv2)

SURR.VAR = sva(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, MODEL0, n.sv = NUM.SV, method = "two-step", B = 30)$sv
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])
